Figures for Paper

### 2021-03-02 paper_figures.Rmd
added nmd
sy5y nmd data sheet and relative script to produce fig 2d

>>>>

# NMD experiment on sy5y cells

for_bar_plot_sy <- read_csv(file.path(here::here(),"data","results_17022021_sy5y.csv"))

for_bar_plot_sy <- data.frame(for_bar_plot_sy)
for_bar_plot_sy$condition <- as.factor(for_bar_plot_sy$condition)
for_bar_plot_sy$condition <- factor(for_bar_plot_sy$condition,levels(for_bar_plot_sy$condition)[c(2,1)])

nmd_plot = ggbarplot(for_bar_plot_sy,
                        x = 'gene',
                        add = c("mean_se","jitter"),
                        y = 'value',
                        fill = 'condition',
                        color = 'condition',
                        position = position_dodge(0.8),
                        dot.size = 10) + 
  scale_y_continuous(labels = scales::percent) + 
  ggpubr::theme_pubr() +
  scale_fill_manual(
    values = c("#40B0A6","#E1BE6A")
  ) + 
  scale_color_manual(
    values = c("#1C2617","#262114")
  )

plot(nmd_plot)
```
